On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-06 AvdMomZvol_rails/Article.tex
[AMZr] Abstract

>>>>

\paragraph{Absctract.}
	An integral point set $\mathcal{P}$ is a set of $n$ points in
	the $m$-dimensional Euclidean space $\mathbb{R}^{m}$ with pairwise
	integral distances,
	such that $\mathcal{P}$ is not contained in a $(m-1)$-dimensional hyperplane.
	In the present paper we present some classes of planar integral point sets ($m=2$);
	we mostly focus on the subsets of a union of two straight lines:
	facher, rails, scissors and pyramid sets.
	We use rails and pyramid sets to construct lower bounds for a diameter
	of integral point sets in higher dimensions.
